The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and its science Implications.

### 2016-02-19 DishSimulations/paper/DishSimulationsPaper_v6.tex

\newcommand{\bx}{{\bf x}}
\newcommand{\bl}{\boldsymbol{\ell}}
\newcommand{\fts}{{\widetilde{s}}}
\newcommand{\ftr}{{\widetilde{r}}}
\newcommand{\ftv}{{\widetilde{v}}}
\newcommand{\bu}{{\bf u}}
\newcommand{\bb}{{\bf b}}
\newcommand{\ftR}{{\widetilde{R}}}

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{color}
\usepackage{hyperref}
\citestyle{aa}

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and their Science Implications}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{6},
Jacqueline Hewitt\altaffilmark{1,2},
Zaki S. Ali\altaffilmark{5},
Judd Bowman\altaffilmark{6},
Carina Cheng\altaffilmark{5},
David Deboer\altaffilmark{5},
Aaron Parsons\altaffilmark{5},
Mariet Venter\altaffilmark{7}
and others.
}

\altaffiltext{1}{MIT Kavli Institute for Cosmological Physics}
\altaffiltext{2}{MIT Dept. of Physics}
\altaffiltext{3}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{4}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
\altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
\altaffiltext{7}{Stellenbosh}
Tempe AZ}
\begin{abstract}
We use time domain electromagnetic simulations to assess the spectral characteristics of the antenna element for the Hydrogen Epoch of Reionization Array (HERA). These simulations are part of a multi-faceted campaign to determine whether the dish's design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization. Our simulations show the existence of standing wave reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity over a small segment of the band. We find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.23$\,$h$Mpc$^{-1}$. Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments such as the Square Kilometer Array. 
\end{abstract}
\section{Introduction}
Observations of the redshift 21\,cm radiation from neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews). Two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized. The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data. The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers. A first generation of such experiments are currently taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations. These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}. Already, these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015,EwallWice:2015a} and significant scientific results. The most stringent measurement of $\approx 500$\,mK$^2$ \citep{Ali:2015} is able to rule out number of scenarios in which the intergalactic medium received little or no heating from X-rays \citep{Pober:2015,Greig:2015b}.

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}. However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal. Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}. While redundant calibration \citep{Wieringa:1992,Liu:2010,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument without deferring to a model. Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperitive to design experiments whose spectral structure is contained, as much as possible, to low delays.

The Hydrogen Epoch of Reionization Array (HERA) is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR \citep{Pober:2014}. Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish. A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination.

This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multi-pronged campaign to assess whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean. We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and ORBCOMM beam mapping \citep{Neben:2016}. In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field.

This paper is organized as follows. In \S~\ref{sec:Formalism} we lay out our analytic framework and describe the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra. In \S~\ref{sec:Simulations} we describe our time-domain electromagnetic simulations of the HERA dish element and how we extract the voltage response function. In \S~\ref{sec:Results} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}. In \S~\ref{sec:Sensitivity} we apply our electromagnetic simulation results to a foreground model to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's ability to constrain reionization parameters. We conclude in \S~\ref{sec:Conclusion}.

\section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window. Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument. Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples with shorter periods. Isolation of the 21\,cm signal from foregrounds that are over four orders of magnitude brighter depends critically on their smoothness. Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself. A simple equation describing effect of direction independent reflections in the signal chain downstream of the feed, has been derived in \citet{EwallWice:2015a}. We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element. 
We start denote the electric field of radiation arriving from direction ${\bf \ell}$ at the $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.

Reflections within the signal chain of each antenna are most generally described by a direction dependent reflection coefficient, $\ftr_i(\bl,\tau)$. Its effect is to add the signal to itself multiplied by $\ftr_i$ and delayed by $\tau$. The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the electric fields arriving from all directions. The presence of the reflections introduces a convolution of the electric field entering the antenna (delayed by $\tau_i$) with $\ftr_i(\bl,\tau)$.

\begin{equation}\label{eq:Voltage}
\ftv_i(t) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) \fts(\bl,t+ \tau_i - \tau)
\end{equation}

The correlator of a radio interferometer records the time-averaged product of the Fourier transfored voltage streams of the $i^{th}$ and $j^{th}$ antennas. Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(f) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,f)e^{-2 \pi i f(\tau_i+\tau)}
\end{equation}
The time averaged product between the two antennas is
\begin{align}
V_{ij}'(f) &= \left \langle v_i(f) v_j^*(f) \right \rangle_t \nonumber \\
 &= \int d \Omega d \tau d \tau' \ftr_i(\bl,\tau) \ftr^*_j(\bl,\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
\end{align}
where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$ and $I(\bl,f)=\left \langle |s(f,\bl)|^2 \right \rangle_t$. Here, we have invoked the fact that electromagnetic waves arriving from different directions are incoherent.

Defining $\bu_{ij} = f (\bx_i-\bx_j)/c$ and performing the $\tau$ and $\tau'$ Fourier transforms, we arrive at
\begin{equation}\label{eq:Visibility}
V'_{ij}(f) =  \int d \Omega r_i(\bl,f) r^*_j(\bl,f)  I(\bl,f)e^{2 \pi i f \bu_{ij} \cdot \bl/c},
\end{equation}
where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ and $r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish. From equation~\ref{eq:Visibility} we see that $r_i(\bl,f)$ is precisely the voltage beam of the antenna. Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.

@@

\widetilde{V}_{ij}(\tau) = \int d f e^{2 \pi i \tau f} V_{ij}(f).

@@

\widetilde{V}'_{ij}(\tau)=  \int d \Omega \int d f  r_i(\bl,f) r_j^*(\bl,f)  I(\bl,f) e^{2 \pi i f ( \bb_{ij} \cdot \bl /c - \tau)}

@@

Let's examine the quantity within the angular integral. We see that each source located at $\bl$ on the sky is mapped to a line $\tau =\bb_{ij}\cdot \bl/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}. The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel

@@

\ftR_{ij}(\bl,\tau) = \int d \tau \ftr_i(\bl,\tau - \Delta \tau) \ftr^*_j(\bl,-\Delta \tau).

@@

which is the convolution of the delay response of the voltage beam of antenna $i$ with the time-reversed complex conjugate of voltage beam of antenna $j$. In the remainder of this paper, we will often refer to $\ftR$ as the {\it power kernel} applied to a visibility. Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays. We demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources. Without reflections, the sources would form lines in $b-\tau$ space. With the reflections, the sources are smeared out, leading to supra-horizon emission. 

@@

\caption{A cartoon demonstration of the impact on foregrounds of the frequency dependent beam. Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element). Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}. Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line. We see that this smearing can lead to substantial supra-horizon emission.}

@@

\widetilde{V}_{ij}'(\tau) = \int d\tau' \int d \tau'' \widetilde{g}_i(\tau' - \tau'')\widetilde{g}^*_j(\tau'') \widetilde{V}_{ij}(\tau-\tau')

@@

where $V_{ij}$ is the visibility for the achromatic voltage pattern, $a_i(\bl)$. 

@@

\widetilde{V}_{ij}'(\tau) &\approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(\tau')\widetilde{V}_{ij}(\tau- \tau') \nonumber \\
& + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}_{ij}(\tau-\tau') 

@@

\section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}

HERA \citep{Pober:2014,DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12). Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa. HERA is meant to serve as a vast improvement in sensitivity over current efforts for only a modest increase in cost. It achieves this by increasing the number of correlated inputs by only a factor of $\approx 2$ while increasing the total collecting area of each correlated element by over an order of magnitude and arranging the elements in such a way as to maximize the number of short baselines that are located outside of the foreground wedge. Central to increasing the collecting area of each element is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes. In Fig.~\ref{fig:AntennaCompare} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
\caption{The HERA antenna element (bottom) uses a parabolic dish to achieve an order of magnitude increase in collecting area over the PAPER antenna (top). The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish. The dish geometry has the potential to introduce intra-antenna reflections which we explore in this work.}
\label{fig:AntennaCompare}
\end{figure}

>>>>

\newcommand{\bx}{{\bf x}}
\newcommand{\bl}{\widehat{\bf r}}
\newcommand{\fts}{{\widetilde{s}}}
\newcommand{\ftr}{{\widetilde{r}}}
\newcommand{\ftv}{{\widetilde{v}}}
\newcommand{\bu}{{\bf u}}
\newcommand{\bb}{{\bf b}}
\newcommand{\ftR}{{\widetilde{R}}}

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{color}
\usepackage{hyperref}
\usepackage{comment}
\citestyle{aa}

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic  Simulations and its science Implications.}
\author{
Aaron Ewall-Wice \altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
David Deboer\altaffilmark{5},
Jacqueline Hewitt\altaffilmark{1,2},
Aaron Parsons\altaffilmark{5},
James Aguirre\altaffilmark{6},
Zaki S. Ali\altaffilmark{5},
Carina Cheng\altaffilmark{5},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{7},
Mariet Venter\altaffilmark{8},
Judd Bowman\altaffilmark{6},
Eloy de Lera Acedo\altaffilmark{9},
Roger Dickenson\altaffilmark{3},
Phillip Doolittle\altaffilmark{3},
Dennis Egan\altaffilmark{3},
Mike Hedrick\altaffilmark{3},
Saul Kohn\altaffilmark{6},
Patrick Schaffner\altaffilmark{3},
John Shelton\altaffilmark{3},
Benjamin Saliwanchik\altaffilmark{10},
Max Tegmark\altaffilmark{1,2}
H.A. Taylor\altaffilmark{3},
Rusty Taylor\altaffilmark{3},
Butch Wirt\altaffilmark{3},
}

\altaffiltext{1}{MIT Kavli Institute for Cosmological Physics}
\altaffiltext{2}{MIT Dept. of Physics}
\altaffiltext{3}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{4}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
\altaffiltext{6}{Dept. of Physics and Astronomy, University of Pennsylvania, Philidelphia, PA}
\altaffiltext{7}{School of Earth and Space Exploration, Arizona State U.Tempe AZ}
\altaffiltext{8}{Cavendish Laboratory, University of Cambridge, Cambridge, UK}
\altaffiltext{9}{SKA South Africa, Cape Town, SA}
\altaffiltext{10}{University of KwaZulu-Natal, Durban, SA}
\begin{abstract}
We use time domain electromagnetic simulations to assess the spectral characteristics of the dish antenna for the Hydrogen Epoch of Reionization Array (HERA). These simulations are part of a multi-faceted campaign to determine whether the dish design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization. Our simulations show the existence of reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity. Even in the presence of this structure, we find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.23$\,$h$Mpc$^{-1}$. Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments.%such as the Square Kilometer Array. 
\end{abstract}
\section{Introduction}
Observations of the redshifted 21\,cm radiation from neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews). Two major experimental endeavors are underway to detect the 21\,cm signal, with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized. The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data. The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers. A first generation of such experiments are currently taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations. These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a}, the MIT Epoch of Reionization Experiment (MITEoR) \citep{Zheng:2013}, and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}. Already, many of these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015} and significant scientific results. The most stringent measurement of $\approx 500$\,mK$^2$ \citep{Ali:2015} is able to rule out number of scenarios in which the intergalactic medium received little or no heating from X-rays \citep{Pober:2015,Greig:2015b}.

The primary challenge to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter \citep{Bernardi:2009,Pober:2013a,Dillon:2014}. While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}. Since the location of each foreground on the sky determines its position in the wedge, with sources near the horizon being introduced at line of sight scales closest to the {\it EoR window}, the angular response of an instruments beam pattern has significant implications on the amount of side-lobe power that is leaked into the EoR window \citep{Thyagarajan:2015a,Thyagarajan:2015b,Pober:2016}.

Beyond leakage from wedge side-lobes, any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the EoR window at small line of sight scales, masking the signal. Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant calibration challenge \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, it is being investigated whether any mismodeling of emission and the primary beam will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}. While redundant calibration \citep{Wieringa:1992,Liu:2010,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, antenna elements with significant direction dependent chromaticity that varies from element to element might break the assumptions of redundancy that such calibration relies upon and pose a significant obstacle. Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperative to design experiments whose band-passes are as devoid of spectral structure as possible.

Drawing off of the lessons of the PAPER, MWA, and MITEoR experiments, the Hydrogen Epoch of Reionization Array (HERA) \citep{Pober:2014,DeBoer:2016} is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR. Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish. A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of the side-lobe contamination observed in \citep{Thyagarajan:2015a,Thyagarajan:2015b,Pober:2016}. Central to increasing the collecting area of each element on HERA is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes. In Fig.~\ref{fig:AntennaCompare} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.

\begin{figure}
\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
\caption{The HERA antenna element (bottom) uses a parabolic dish to achieve an order of magnitude increase in collecting area over the PAPER antenna (top). The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish. The suspended feed arrangement has the potential to introduce intra-antenna reflections which we explore in this work.}
\label{fig:AntennaCompare}
\end{figure}

This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multi-pronged campaign to assess whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean. We accomplish this by establishing antenna specifications with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that the HERA primary antenna element meets these specifications with reflectometry \citep{Patra:2016} and ORBCOMM beam mapping \citep{Neben:2016}. In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field.

This paper is organized as follows. In \S~\ref{sec:Formalism} we lay out our analytic framework and describe the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra. In \S~\ref{sec:Simulations} we describe our time-domain electromagnetic simulations of the HERA dish element and how we extract the voltage response function. In \S~\ref{sec:Results} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}. In \S~\ref{sec:Sensitivity} we apply our electromagnetic simulation results to a foreground model to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and the impact on HERA's ability to constrain reionization parameters. We summarize our conclusions in \S~\ref{sec:Conclusion}.

\section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window. Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument. Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples with shorter periods. Isolation of the 21\,cm signal from foregrounds that are over four orders of magnitude brighter depends critically on their smoothness. Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself. A simple equation describing the effect of direction independent reflections in the signal chain downstream of the feed has been derived in \citet{EwallWice:2015a}. We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element. 
We start by denoting the electric field of radiation arriving from direction ${\bf \ell}$ at the $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.

Reflections within the signal chain of each antenna are most generally described by a direction dependent reflection coefficient, $\ftr_i(\bl,\tau)$. Its effect is to add the signal to itself multiplied by $\ftr_i$ and delayed by $\tau$. The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the electric fields arriving from all directions. The presence of reflections introduces a convolution of the electric field entering the antenna (delayed by $\tau_i$) with $\ftr_i(\bl,\tau)$:

\begin{equation}\label{eq:Voltage}
\ftv_i(t) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) \fts(\bl,t- \tau_i - \tau).
\end{equation}
Applying the Fourier convolution theorem, the Fourier transform of this equation gives $v_i(\omega)$ as the simple angular integral of the product of $s_i(\bl,\omega)$ and $r_i(\bl,\omega)$, where $\omega=$ is the angular frequency of electromagnetic radiation.
\begin{equation}
v_i(\omega) = \int d \Omega  r_i(\bl,\omega) s(\bl,\omega) e^{-i \omega \tau_i}.
\end{equation}

The correlator of a radio interferometer records the time-averaged product of the Fourier transfored voltage streams of the $i^{th}$ and $j^{th}$ antennas. 
\begin{comment}
Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(\omega) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,\omega)e^{-i \omega (\tau_i+\tau)}.
\end{equation}
\end{comment}
The time averaged product of the Fourier transform between the two antennas is
\begin{align}\label{eq:Visibility}
V_{ij}'(\omega) &= \left \langle v_i(\omega) v_j^*(\omega) \right \rangle_t \nonumber \\
 &= \int d \Omega r_i(\bl,\omega) r_j^*(\bl,\omega) I(\bl, \omega) e^{- i\omega\Delta \tau_{ij}} \nonumber \\
 & = \int d \Omega r_i(\bl,\omega) r^*_j(\bl,\omega)  I(\bl,\omega)e^{-i\omega \bb_{ij} \cdot \bl/c},
\end{align}
where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$, $I(\bl,\omega)=\left \langle |s(\bl,\omega)|^2 \right \rangle_t$, and $\bb_{ij} = (\bx_i-\bx_j)$. Here, we have invoked the fact that electromagnetic waves arriving from different directions are incoherent. This equation leaves us with the familiar interferometry equation \citep{Thompson:1986}, allowing us to see that $r_i(\bl,\omega)$ equivalent to the voltage beam of the antenna. Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.

@@

\widetilde{V}_{ij}(\tau) = \frac{1}{2 \pi} \int d \omega V_{ij}(\omega) e^{i \omega \tau }.

@@

\widetilde{V}_{ij}(\tau)= \frac{1}{2\pi} \int d \Omega \int d \omega r_i(\bl,\omega) r_j^*(\bl,\omega)  I(\bl,\omega) e^{-i \omega ( \bb_{ij} \cdot \bl /c - \tau)}.

@@

Let's examine the quantity within the angular integral. We see that each source located at $\bl$ on the sky is mapped to a line $\tau =\bb_{ij}\cdot \bl/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}. The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel,

@@

\ftR_{ij}(\bl,\tau) = \int d  \tau' \ftr_i(\bl,\tau - \tau') \ftr^*_j(\bl,-\tau'),

@@

which is the convolution of the delay response of the voltage beam of antenna $i$ with the time-reversed complex conjugate of voltage beam of antenna $j$. In the remainder of this paper, we will often refer to $\ftR$ as the {\it power kernel} applied to a visibility. Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays. We demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources. Without reflections, the sources would form lines intersecting zero in the two dimensional space with the baseline length, $b$ on the x-axis and the delay, $\tau$ on the y-axis. With the reflections, the sources are smeared out, leading to supra-horizon emission. 

@@

\caption{A cartoon demonstration of the impact on foregrounds of the frequency dependent beam. Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element). Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}. Since the frequency response of the dish is a function of direction on the sky, the shape of the delay kernel is different for each source line. We see that this smearing can lead to substantial supra-horizon emission.}

@@

\widetilde{V}_{ij}(\tau) = \int d\tau' \int d \tau'' \widetilde{g}_i(\tau' - \tau'')\widetilde{g}^*_j(-\tau'') \widetilde{V}_{ij}^a(\tau-\tau'),

@@

where $V_{ij}^a$ is the visibility for the achromatic voltage pattern, $a_i(\bl)$. 

@@

\widetilde{V}_{ij}(\tau) &\approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(-\tau')\widetilde{V}^a_{ij}(\tau- \tau') \nonumber \\
& + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}^a_{ij}(\tau-\tau').

@@

\section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}
%HERA \citep{Pober:2014,DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12). Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa. HERA is meant to serve as a vast improvement in sensitivity over current efforts for only a modest increase in cost. It achieves this by increasing the number of correlated inputs by only a factor of $\approx 2$ while increasing the total collecting area of each correlated element by over an order of magnitude and arranging the elements in such a way as to maximize the number of short baselines that are located outside of the foreground wedge.

@@

\subsection{The Simulations}\label{ssec:Simulations}
 The time-dependent electromagnetic behavior of the antenna was modeled using Microwave Studio, a commercial numerical simulation package produced by Computer Simulation Technology (CST).  The model consists of an idealized 14 m diameter paraboloid reflector with a feed structure placed at the focus (4.5 m above the surface). The feed was a dual linear polarized sleeved dipole identical to that used as an element of PAPER but with a cylindrical skirt used in place of the angled planar reflectors.   The dipole arms were modeled as copper tubing and aluminum was assigned to the disks and reflector surfaces.  For simulation, the entire model was encapsulated in vacuum dielectric with radiative boundaries and discrete ports of 125\,$\Omega$ impedance were defined at the terminals of the orthogonal dipoles. The simulated is conducted in a box encapsulating the dish geometry plus three wavelengths (at 150\,MHz) on all sides with open boundary conditions.
